A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-21 sections/Discussion.tex
minor edit

But there are issues about the well-formedness condition.
Normally $\Gm \vdash_{wf} (e : A)$ is defined by $\Gm \vdash_{wf} e$ and $\Gm \vdash_{wf} A$.
When $A = \all A'$, the type variable $a$ is not introduced to the context of $e$,
therefore $\Gm \vdash_{wf} e$ is not derivable.

To address the problem, one can either
1) change the well-formedness judgment by introducing the binder for terms as well;
or 2) add a syntax that explicitly bind the generic type variable.
The former approach requires to resolve overlapping cases
$(e : \all A)$ with $(e : B)$ where $B \neq \all B'$.
Therefore we choose the latter approach due to its simplicity.
The syntax of expression is extended with one more constructor:
$$
\begin{array}{l@{\qquad}lcl}
\text{Expressions}\qquad&e &::=&\quad x \mid () \mid \lam e \mid e_1~e_2 \mid (e:A) \mid \Lambda a.~e:A
\end{array}
$$

Notice that the type-lambda syntax $\Lambda a.~e:A$ annotates the generic function $e$ with $\all A$,
while making $a$ visible inside the body of the function.
Corresponding rules are introduced for both the declarative system and the algorithmic system:
$$
\inferrule*[right=$\mathtt{Decl}\Lambda$]
    {\Psi,a \vdash A \quad \Psi,a \vdash e\Lto A}
    {\Psi\vdash \Lambda a.~e:A \To \all A}
$$
$$\Gm \Vdash \Lambda a.~e:A \To_b \jg \algrule \Gm \Vdash [(\all A)/b]\jg, a \Vdash e \Lto A$$

The new syntax for expressions also affect the well-formedness judgment:
$$
\inferrule*[right=$\mathtt{wf\_}\Lambda$]
    {\Gm,a \vdash_{wf} e \quad \Gm,a \vdash_{wf} A}
    {\Gm \vdash_{wf} \Lambda a.~e:A}
$$

>>>>

But there are issues about the well-formedness condition.
Normally $\Psi \vdash (e : A)$ is defined by $\Psi \vdash e$ and $\Psi \vdash A$.
However, when $A = \all A'$, the type variable $a$ is not introduced to the context of $e$,
therefore $\Psi \vdash e$ is not derivable.

To address the problem,
we add a syntax that explicitly bind the generic type variable into a function and its annotation.
The syntax of expression is extended with one more constructor:
$$
\begin{array}{l@{\qquad}lcl}
\text{Expressions}\qquad&e &::=&\quad x \mid () \mid \lam e \mid e_1~e_2 \mid (e:A) \mid \Lambda a.~e:A
\end{array}
$$

The new type-lambda syntax $\Lambda a.~e:A$ actually annotates the generic function $e$ with $\all A$,
while making $a$ visible inside the body of the function.
The well-formedness judgments are updated naturally:
$$
\inferrule*[right=$\mathtt{wf_d}\Lambda$]
    {\Psi,a \vdash e \quad \Psi,a \vdash A}
    {\Psi \vdash \Lambda a.~e:A}
\qquad
\inferrule*[right=$\mathtt{wf\_}\Lambda$]
    {\Gm,a \vdash e \quad \Gm,a \vdash A}
    {\Gm \vdash \Lambda a.~e:A}
$$

Corresponding rules are introduced for both the declarative system and the algorithmic system:
$$
\inferrule*[right=$\mathtt{Decl}\Lambda$]
    {\Psi,a \vdash A \quad \Psi,a \vdash e\Lto A}
    {\Psi\vdash \Lambda a.~e:A \To \all A}
$$
$$\Gm \Vdash \Lambda a.~e:A \To_b \jg \algrule \Gm \Vdash [(\all A)/b]\jg, a \Vdash e \Lto A$$
